\problemname{Early Exam Evacuation}

You find yourself writing an exam in a long, narrow auditorium -- it has $N$ $(1 \leq N \leq 10^5)$
rows, numbered $1, ..., N$ from the front to the back, each of which has $5$ seats, $3$ on each side
of the aisle running down the middle of the auditorium. Each seat is identified by its row number
immediately followed by a letter from "A" to "F", which indicates its position in that row (with
seat "A" at the far left, and "F" at the far right). The aisle lies between seats "C" and "D" in
each row. The auditorium also has two secure rooms -- one at the front (in front of row 1), and one
at the back (behind row $N$).

Every seat in the auditorium is initially occupied by exactly one exam-writer per seat. However,
over the course of the exam, $M$ different exam writers decide that they have written all they can
on the exam, and then would like to leave the auditorium, one after another. The $i$th exam writer
is in seat $R_iC_i$ ($1 \leq R_i \leq N, C_i$ is one of A, \ldots, F). When the exam writer leaves
the auditorium, they must stay in one of the secure rooms until the end of the exam. Fortunately,
both secure rooms can hold as many people as necessary.

Exam writers not only worry about writing exams, but they would like their lives to be as convenient
as possible -- as such, they're interesting in working together to minimize the total inconvenience
experienced by all of them. The inconvenience a single exam-writer experiences is $Ax+By$, where $A$
and $B$ are given constants $(0 \leq A,B \leq 10^9)$, $x$ is the number of different people passed
on the way to the chosen secure room (explained below), and $y$ is the number of people already in
that secure room before that exam-writer enters. Note that if an exam-writer does not leave their
seat, their inconvenience is $0$.

When walking from a seat to a secure room, one must first pass any other exam writers in the same
row on the way to the aisle, and then any exam writers in seats adjacent to the aisle from that row
to either row $1$ or $N$ (depending on which secure room is chosen), inclusive. Note that any vacant
seats passed along the way don't count towards this value.

Can you help the poor exam writers make their lives as convenient as possible?

\section*{Input}
The first line contains four space-separated integers: $N$ $(1 \leq N \leq 10^5)$, the number of rows
in the auditorium; $M$ $(1 \leq M \leq 6N)$, the number of exam writers that leave early; $A$,
followed by $B$ $(1 \leq A,B \leq 10^9)$, the constants used in determining the inconvenience caused
by an exam writer leaving early.

The next $M$ lines each contain one integer followed by one character, $R_i$ and $C_i$, for $i =
1, \ldots, N$ in order, where $1 \leq R_i \leq N$ and $C_i \in \{A, \ldots, F\}$.

For partial credit, you may assume that $M \leq 5000$.

\section*{Output}
Output the integer which is the minimum total inconvenience experienced by all $M$ exam writers who
leave early.
