\problemname{Hopper}

A hopper is a virtual creature that visits Java programs and explores their arrays. Scientists
observed a hopper and came to the following conclusions:
\begin{itemize}
\item a hopper only visits arrays with integer entries, 
\item a hopper always explores a sequence of array elements using the
  following rules:
  \begin{itemize}
  \item a hopper cannot jump too far, that is, the next element is
    always at most $D$ indices away (how far a hopper can jump depends
    on the length of its legs),
  \item a hopper doesn’t like big changes in values---the next element
    differs from the current element by at most $M$, more precisely
    the absolute value of the difference is at most $M$ (how big a
    change in values a hopper can handle depends on the length of its
    arms), and
  \item a hopper never visits the same element twice.
  \end{itemize}
\item a hopper will explore the array with the longest exploration
  sequence.
\end{itemize}
The scientists now need to prepare arrays for further study of hoppers and they need your
help. They want a program that given an array and values D and M computes the length
of the longest exploration sequence in the array.

\section*{Input}

The first line contains $k$, the number of problems. Then descriptions
of the problems follow.  Each problem is described on two lines. The
first line of a problem description contains three numbers $n$, $D$,
$M$, where $n$ is the length of the array (as described above, $D$ is
the maximum length of a jump the hopper can make, and $M$ is the
maximum difference in values a hopper can handle). The next line
contains $n$ integers---the entries of the array. We have
$1 \leq D \leq 7$, $1 \leq M \leq 10\,000$, $1 \leq n \leq 10\,000$
and the integers in the array are between $-1\,000\,000$ and
$1\,000\,000$.

\section*{Output}

The output contains one line for each problem—the length of the
longest exploration sequence. The hopper can start and end at any
location and the length is computed as the number of visited
locations.
