\problemname{Werewolf}
As they usually do, $N$ robots are playing the game of Werewolf, and the robots are numbered with integers from $1$ to $N$. Exactly $W$ of these robots are werewolves, and the remainder are civilians. Though the game of Werewolf involves various aspects, we will focus on a single discussion phase of the game.

Robots accuse other robots of being werewolves and defend other robots by vouching for their innocence.

The werewolves know each other's identities and:

\begin{itemize}
\item a werewolf never accuses another werewolf;
\item any robot that a werewolf defends is another werewolf.
\end{itemize}

Civilians may accuse or defend either type of robot.
Additional constraints make our task a bit easier:

\begin{itemize}
\item No robot is both accused and defended.
\item No robot is accused or defended more than once.
\item For a robot $A$ to accuse or defend robot $B$, then $A < B$.
\end{itemize}

You will be given all the accusations and defenses between N robots where there are exactly $W$ werewolves. A role assignment identifies each of the robots as either werewolf or civilian. Your goal is to figure out how many role assignments satisfy all the above constraints.

\section*{Input}
The first line contains three numbers (each separated by one space):

\begin{itemize}
\item $N$ $(1 \leq N \leq 200)$, the number of robots, followed by
\item $W$ $(0 \leq W \leq N)$, the number of werewolves, followed by
\item $M$ $(0 \leq M < N)$, the number of accusations/defenses.
\end{itemize}

The next $M$ lines give the accusations and defenses. Each of these lines will be one of the following two forms:

\begin{itemize}
\item $A$ $a$ $b$ indicates robot $a$ accused robot $b$ of being a werewolf;
\item $D$ $a$ $b$ indicates robot $a$ defended robot $b$.
\end{itemize}

For partial credit, you may assume that $N \leq 20$.

\section*{Output}
Output the number of role assignments that are consistent with the given information. Since this number may be very large, you must output this answer modulo $10^9 + 7$.
